---
title: "Affective Signaling: Analysis"
author: "Miklos Bognar"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r load packages, warning = FALSE, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, osfr, lme4, lmerTest, MuMIn, BayesFactor, DescTools, sjstats, car, broom, papaja, forcats)
```

# Load helper functions

```{r load helper functions}
source("../utils.R")
```

# Current version

```{r}
current_version = "affective_primeprobe_valence_source_data"
```

# Load data
```{r}
# Reaction time
processed_rt <- read_tsv(file.path(current_version, "data", "Processed", "aspp_valence_rt_processed.tsv"))
processed_rt_nmin3 <- read_tsv(file.path(current_version, "data", "Processed", "aspp_valence_rt_nmin3_processed.tsv"))

```

# Descriptive statistics of the sample size
## Number of participants left after exclusion

The number of participants is the same for the reaction time, the accuracy analyses as well.

```{r}
processed_rt %>% 
  distinct(participant_id) %>% 
  count()
```

## Number of responses after exclusion
### For the reaction time analysis

```{r}
processed_rt %>%
  count()
```


## Age

We calculated the following statistics based on the reaction time data file, but because it contains the same participants as the accuracy data files there should be no difference between the results.

```{r}
processed_rt %>% 
  distinct(participant_id, .keep_all = T) %>% 
  summarize(median_age = median(age, na.rm = T),
            min_age = min(age, na.rm = T),
            max_age = max(age, na.rm = T),
            quart1_age = quantile(age, probs = 0.25, na.rm = T),
            quart3_age = quantile(age, probs = 0.75, na.rm = T)) %>% 
  knitr::kable(caption = "Age demographics")
```

## Gender

```{r}
processed_rt %>% 
  distinct(participant_id, .keep_all = T) %>% 
  group_by(gender) %>% 
  count() %>% 
  ungroup() %>% 
  filter(gender %in% c("female", "male")) %>% 
  mutate(prop = n / sum(n) * 100) %>% 
  knitr::kable(caption = "Gender demographics")
```



## Education demographics

```{r}
processed_rt %>% 
  distinct(participant_id, .keep_all = T) %>% 
  group_by(education) %>% 
  count() %>% 
  ungroup() %>% 
  filter(education %ni% c("blank", "refused")) %>% 
  mutate(prop = n / sum(n) * 100) %>% 
  knitr::kable(caption = "Education demographics")
```

# Investigating the effects of the words
## Reaction time

```{r}
processed_rt %>% 
  mutate(valency = case_when(is_prev_cong == 1 ~ "Neutral",
                             is_prev_cong == 0 ~ "Negative")) %>%
  group_by(word_content, valency) %>%
  summarize(n_occurence = n(),
            mean_rt = mean(rt)) %>% 
  arrange(mean_rt) %>% 
  ggplot() +
  aes(x = word_content, y = mean_rt, color = valency) +
  geom_point() +
  labs(y = "Mean reaction time",
       x = "Words",
       color = "Valency of\nthe word") +
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank())
```

# Figures of affective-congruency sequence effect

## For the reaction time data

```{r}
# Prepare data for plotting
cse_plot_rt_data <- 
  processed_rt %>% 
  mutate(is_prev_cong = case_when(is_prev_cong ==  0L ~ "Negative",
                                  is_prev_cong ==  1L ~ "Neutral"),
         is_prev_cong = as_factor(is_prev_cong),
         is_prev_cong = fct_relevel(is_prev_cong, c("Neutral", "Negative")),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_prev_cong, is_congruent) %>% 
  summarise(participant_mean_rt = mean(rt, na.rm = T)) %>% 
  group_by(is_prev_cong, is_congruent) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

# Create the plot
cse_plot_rt <- 
  cse_plot_rt_data %>% 
  ggplot() +
  aes(x = is_prev_cong,
                 y = mean_rt,
                 shape = is_congruent,
                 group = is_congruent) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(550, 800)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Valence of the previous word")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "Congruency of \n the current trial")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.5,0.85),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        )

# Print the plot
cse_plot_rt
```

#Save the figure
```{r}
ggsave(file.path(current_version, "figures/prime_probe_valence_rt_cse.png"), width = 14.4, height = 8, plot = last_plot())
```

#regression model on rt prediction

```{r}
#random intercept model without any predictors
rt_random_model <- lmer(rt ~ 1 + (1|filename), data = processed_rt)

#congruency effect linear model
rt_random_intercept_model_congruency <- lmer(rt ~ is_congruent + (1|filename), data = processed_rt)
rt_random_intercept_slope_model_congruency <- lmer(rt ~ is_congruent + (1+is_congruent|filename), data = processed_rt)

#checking with random slope
congruency_effect_summary <- summary(rt_random_intercept_model_congruency)
congruency_effect_summary_random_slope <- summary(rt_random_intercept_slope_model_congruency)
congruency_effect_summary
```

#Bayesian analysis of congruency main effect

```{r}
Bf(sd = congruency_effect_summary$coefficients[4],
   obtained = congruency_effect_summary$coefficients[2]*-1,
   dfdata = congruency_effect_summary$coefficients[6],
   meanoftheory = 0,
   sdtheory = 73, # 73ms is the congruency effect obtained in Weissman et al (2014) on prime probe
   dftheory = 10^10,
   tail = 1)

```

#regression model for previous word valence and current trial congruency interaction

```{r}
rt_random_intercept_slope_model_interaction <- lmer(rt ~  is_congruent * is_prev_cong + (1+is_congruent|filename), data = processed_rt) 
rt_random_intercep_model_interaction <- lmer(rt ~  is_congruent * is_prev_cong + (1|filename), data = processed_rt) 
interaction_effect <- summary(rt_random_intercept_slope_model_interaction)
interaction_effect
```

#Bayesian analysis of interaction effect

```{r}
Bf(sd = interaction_effect$coefficients[8],
   obtained = interaction_effect$coefficients[4]*-1,
   dfdata = interaction_effect$coefficients[12],
   meanoftheory = 0,
   sdtheory = 36.5,#RR[3.8, infinite],36.5 - half of the congruency effect obtained in Weissman et al (2014)
   dftheory = 10^10,
   tail = 1)

```

# Main effect in the same linear regression
```{r}
Bf(sd = interaction_effect$coefficients[6],
   obtained = interaction_effect$coefficients[2]*-1,
   dfdata = interaction_effect$coefficients[10],
   meanoftheory = 0,
   sdtheory = 73,#27692,#0.35, # 73ms is the congruency effect obtained in Weissman et al (2014) on prime probe
   dftheory = 10^10,
   tail = 1)

```

## Exploratory sequential effect analysis
```{r}
sequential_cse_data = read_tsv(file.path(current_version, "data", "Processed", "sequential_cse_processed.tsv"))

sequential_cse_model = lmer(rt ~ n_min3_cong * is_congruent + (1+is_congruent|participant_id), sequential_cse_data)
sequential_cse_summary = summary(sequential_cse_model)
sequential_cse_summary
```



```{r}
# congruency effect

Bf(sd = sequential_cse_summary$coefficients[7],
   obtained = sequential_cse_summary$coefficients[3]*-1,
   dfdata = sequential_cse_summary$coefficients[11],
   meanoftheory = 0,
   sdtheory = 73, 
   dftheory = 10^10,
   tail = 1)
```

```{r}
# congruency sequence effect

Bf(sd = sequential_cse_summary$coefficients[8],
   obtained = sequential_cse_summary$coefficients[4]*-1,
   dfdata = sequential_cse_summary$coefficients[12],
   meanoftheory = 0,
   sdtheory = 36.5,#5889,#0.8,#36.5, #needs RR
   dftheory = 10^10,
   tail = 1)
```


```{r}
cse_predicted = sequential_cse_data %>% 
  mutate(predicted_rt = predict(sequential_cse_model))

sequential_cse_plot_data <- 
  cse_predicted %>% 
  mutate(n_min3_cong = case_when(n_min3_cong ==  0L ~ "Incongruent",
                                 n_min3_cong ==  1L ~ "Congruent"),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_congruent, n_min3_cong) %>% 
  summarise(participant_mean_rt = mean(predicted_rt, na.rm = T)) %>% 
  group_by(is_congruent, n_min3_cong) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

sequential_cse_plot <- 
  sequential_cse_plot_data %>% 
  ggplot() +
  aes(x = n_min3_cong,
                 y = mean_rt,
                 color = is_congruent,
                 group = is_congruent) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(550, 800)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("congruency of previous trial")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "Congruency of \n the current trial")) +
 papaja::theme_apa() +
  theme(legend.position = c(0.5,0.25),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        )

sequential_cse_plot
```


```{r}
cohen_effect_data = read_tsv(file.path(current_version, "data", "Processed", "cohen_effect_processed.tsv"))

cohen_effect_model = lmer(rt ~ n_min3_cong * is_prev_cong +(1+is_congruent|participant_id), cohen_effect_data)
cohen_summary = summary(cohen_effect_model)
cohen_summary
```

```{r}
Bf(sd = cohen_summary$coefficients[8],
   obtained = cohen_summary$coefficients[4],
   dfdata = cohen_summary$coefficients[12],
   meanoftheory = 0,
   sdtheory = 10,
   dftheory = 10^10,
   tail = 1)
```

```{r}
cohen_predicted = cohen_effect_data %>% 
  mutate(predicted_rt = predict(cohen_effect_model))
cse_plot_rt_data_cohen <- 
  cohen_predicted %>% 
  mutate(is_prev_cong = case_when(is_prev_cong ==  0L ~ "Negative",
                                  is_prev_cong ==  1L ~ "Neutral"),
          is_prev_cong = fct_relevel(is_prev_cong, c("Neutral", "Negative")),
         n_min3_cong = case_when(n_min3_cong ==  0L ~ "Incongruent",
                                 n_min3_cong ==  1L ~ "Congruent"),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_prev_cong, n_min3_cong) %>% 
  summarise(participant_mean_rt = mean(predicted_rt, na.rm = T)) %>% 
  group_by(is_prev_cong, n_min3_cong) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

cse_plot_rt_cohen <- 
  cse_plot_rt_data_cohen %>% 
  ggplot() +
  aes(x = n_min3_cong,
                 y = mean_rt,
                 color = is_prev_cong,
                 group = is_prev_cong) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(550, 800)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Valence of the previous word")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "Congruency of \n the current trial")) +
 # papaja::theme_apa() +
  theme(legend.position = c(0.5,0.25),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        )
# Print the plot
cse_plot_rt_cohen

ggsave(file.path(current_version, "figures/cse_plot_rt_cohen2.png"), width = 14.4, height = 8, plot = last_plot())
```



```{r}
threeway_data = read_tsv(file.path(current_version, "data", "Processed", "threeway_interaction_processed.tsv"))
threeway_model = lmer(rt ~ is_congruent * n_min3_cong * n_min4_valence + (1+is_congruent|filename), data = threeway_data)
threeway_summary = summary(threeway_model)
threeway_summary
```


```{r}
Bf(sd = threeway_summary$coefficients[16],
   obtained = threeway_summary$coefficients[8]*-1,
   dfdata = threeway_summary$coefficients[24],
   meanoftheory = 0,
   sdtheory = 10,
   dftheory = 10^10,
   tail = 1)
```


```{r}
threeway_predicted = threeway_data %>% 
  mutate(predicted_rt = predict(threeway_model))

cse_plot_3way_nmin4_data <- 
  threeway_predicted %>% 
  mutate(is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent"),
n_min3_cong = case_when(n_min3_cong ==  0L ~ "Incongruent",
                                 n_min3_cong ==  1L ~ "Congruent"),
n_min4_valence = case_when(n_min4_valence ==  0L ~ "Negative",
                                  n_min4_valence ==  1L ~ "Neutral"),
 n_min4_valence = fct_relevel(n_min4_valence, c("Neutral", "Negative")),)%>%
  
  group_by(participant_id, is_congruent, n_min3_cong, n_min4_valence) %>% 
  summarise(participant_mean_rt = mean(predicted_rt, na.rm = T)) %>% 
  group_by(is_congruent, n_min3_cong, n_min4_valence) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

cse_plot_3way_nmin4 <- 
  cse_plot_3way_nmin4_data %>% 
  ggplot() +
  aes(x = n_min3_cong,
                 y = mean_rt,
                 color = is_congruent,
      
                 group = is_congruent) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(550, 800)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("nmin3 congruency")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "current congruency")) +
  #papaja::theme_apa() +
  theme(legend.position = c(0.5,0.25),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        )+
  facet_grid(cols = vars(n_min4_valence))

cse_plot_3way_nmin4

ggsave(file.path(current_version, "figures/cse_plot_3way_nmin4.png"), width = 14.4, height = 8, plot = last_plot())

```


```{r}
threeway_between_data = read_tsv(file.path(current_version, "data", "Processed", "threeway_between_processed.tsv"))
threeway_between_model = lmer(rt ~ is_congruent * n_min3_cong * is_prev_cong + (1+is_congruent|filename), data = threeway_between_data)
threeway_between_summary = summary(threeway_between_model)
threeway_between_summary
```

```{r}
Bf(sd = threeway_between_summary$coefficients[16],
   obtained = threeway_between_summary$coefficients[8],
   dfdata = threeway_between_summary$coefficients[24],
   meanoftheory = 0,
   sdtheory = 10,
   dftheory = 10^10,
   tail = 1)
```


```{r}
threeway_between_predicted = threeway_between_data %>% 
  mutate(predicted_rt = predict(threeway_between_model))

cse_plot_3way_between_data <- 
  threeway_between_predicted %>% 
  mutate(is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent"),
n_min3_cong = case_when(n_min3_cong ==  0L ~ "Incongruent",
                                 n_min3_cong ==  1L ~ "Congruent"),
is_prev_cong = case_when(is_prev_cong ==  0L ~ "Negative",
                                  is_prev_cong ==  1L ~ "Neutral"),
 is_prev_cong = fct_relevel(is_prev_cong, c("Neutral", "Negative")),)%>%
  
  group_by(participant_id, is_congruent, n_min3_cong, is_prev_cong) %>% 
  summarise(participant_mean_rt = mean(predicted_rt, na.rm = T)) %>% 
  group_by(is_congruent, n_min3_cong, is_prev_cong) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

cse_plot_3way_between <- 
  cse_plot_3way_between_data %>% 
  ggplot() +
  aes(x = n_min3_cong,
                 y = mean_rt,
                 color = is_congruent,
      
                 group = is_congruent) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(900, 1150)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("nmin3 congruency")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "current congruency")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.5,0.25),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        )+
  facet_grid(cols = vars(is_prev_cong))

cse_plot_3way_between

ggsave(file.path(current_version, "figures/cse_plot_3way_nmin4.png"), width = 14.4, height = 8, plot = last_plot())
```


# Accuracy analysis

```{r}
acc_processed = read_tsv(file.path(current_version, "data", "Processed", "aspp_valence_acc_processed.tsv"))
affective_model = glmer(as.factor(is_correct) ~ as.factor(is_prev_cong) * as.factor(is_congruent) + (1| participant_id), acc_processed, family=binomial)

affective_summary = summary(affective_model)
summary(affective_model)
```

```{r}
Bf(sd = affective_summary$coefficients[8],
   obtained = affective_summary$coefficients[4],
   dfdata = 30322,
   meanoftheory = 0,
   sdtheory = 0.1,
   dftheory = 10^10,
   tail = 1)
```
```{r}
Bf(sd = affective_summary$coefficients[7],
   obtained = affective_summary$coefficients[3],
   dfdata = 30322,
   meanoftheory = 0,
   sdtheory = 0.2,
   dftheory = 10^10,
   tail = 1)
```

```{r}
accuracy_predicted = acc_processed %>% 
  mutate(predicted_acc = predict(affective_model, type="response"))

accuracy_cse_data <- 
  accuracy_predicted %>% 
  mutate(is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent"),
is_prev_cong = case_when(is_prev_cong ==  0L ~ "Negative",
                                  is_prev_cong ==  1L ~ "Neutral"),
 is_prev_cong = fct_relevel(is_prev_cong, c("Neutral", "Negative")),)%>%
  
  group_by(participant_id, is_congruent, is_prev_cong) %>% 
  summarise(participant_mean_acc = mean(predicted_acc, na.rm = T)) %>% 
  group_by(is_congruent,  is_prev_cong) %>% 
  summarise(N = n(),
            mean_acc = mean(participant_mean_acc, na.rm = T),
            sd_acc = sd(participant_mean_acc, na.rm = T),
            se_acc = sd_acc / sqrt(N))

cse_plot_accuracy <- 
  accuracy_cse_data %>% 
  ggplot() +
  aes(x = is_prev_cong,
                 y = mean_acc,
                 shape = is_congruent,
      
                 group = is_congruent) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_acc - se_acc,
                    ymax = mean_acc + se_acc),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(0.93, 0.98)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Valence of previous word")+
  ylab("Accuracy %") +
  guides(shape = guide_legend(title = "Congruency of \n the current trial")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.5,0.25),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        )

cse_plot_accuracy

ggsave(file.path(current_version, "figures/accuracy_plot.png"), width = 14.4, height = 8, plot = last_plot())
```

