---
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r load packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, osfr, janitor, lubridate, purrrlyr)
```

# Load helper functions

```{r load helper functions}
source("../utils.R")
```

# Current version of the design

```{r}
current_version <- "global_core_flanker"
```

Currently we are working with the following version of the design: `r str_extract(current_version, "[^/]+$")`

# Create local data structure

```{r}
local_data_pth <- file.path(current_version, "data")

create_local_structure(local_data_pth)
```

# Import data from OFS

```{r}
raw_folder = file.path(local_data_pth, "Raw")

# These are for private nodes, public nodes doesn't need authentication
token = readLines("../osf_token")
osf_auth(token)

myfile = osf_retrieve_node("e6waf") %>%
  osf_ls_files() %>% 
  filter(name == "flanker_raw_data.tsv")

osf_download(myfile, raw_folder)

raw = read_tsv(file.path(raw_folder, "flanker_raw_data.tsv"))

```


# Import data from local

```{r, echo=F}
raw <- read_tsv(file.path(current_version, "data", "Raw", "flanker_raw_data.tsv"))
```

# Check whether each participant completed the study
## Number of trials for the primeprobe task

** practice = 24
** test = 388
** total = 412

Blocks:
1 - 24
2 - 105
3 - 186
4 - 267

```{r}
raw %>% 
  group_by(participant_id, is_practice) %>% 
  count() %>%
  mutate(complete = case_when(is_practice == 1L & n == 24 ~ "complete",
                              is_practice == 0L & n == 388 ~ "complete",
                              TRUE ~ "incomplete")) %>% 
  group_by(is_practice, complete) %>% 
  count()
```

# Save practice trials to a separate df

```{r save practice trials}
practice <-
  raw %>%
  filter(is_practice == 1L)
```

# Save test trials to a separate df

```{r save test trials}
test <-
  raw %>%
  filter(is_practice == 0L)
```

# Calculate accuracy in each task for each participant

```{r calculate accuracy}
test <-
  test %>%
  mutate(is_correct = case_when(response_target == response_content ~ 1L,
                                response_target != response_content ~ 0L)) %>%
  group_by(participant_id) %>% 
  mutate(prop = sum(is_correct) / n() * 100,
         drop_participant_acc = case_when(prop < 70 ~ 1L,
                                          TRUE ~ 0L))

test %>%
  group_by(drop_participant_acc, participant_id) %>% 
  summarize() %>% 
  count()

mean(test$prop)
```

# Calucalte the response time variable

```{r calculate response time}
test <-
  test %>% 
  mutate(rt = case_when(response_content != "TIMEOUT" ~ response_time - stim_onset,
                        response_content == "TIMEOUT" ~ NA_real_))
```

# Add variables storing whether the previous trials were congruent and correct

```{r previous congruency}
test <-
  test %>% 
  mutate(is_prev_congruent = case_when(trial_id == 24 ~ NA_integer_,
                                       trial_id > 24 & lag(is_congruent) == 1L ~ 1L,
                                       trial_id > 24 & lag(is_congruent) == 0L ~ 0L),
         is_prev_correct = case_when(trial_id == 24 ~ NA_integer_,
                                     trial_id > 24 & lag(is_correct) == 1L ~ 1L,
                                     trial_id > 24 & lag(is_correct) == 0L ~ 0L))
```

# Exclude participants where all the trials are time out trials

```{r}
rt_all_missing <-
  test %>% 
  group_by(participant_id) %>% 
  summarise(drop_all_missing_rt = case_when(all(is.na(rt)) ~ 1L,
                                            TRUE ~ 0L))
rt_all_missing %>% 
  group_by(participant_id, drop_all_missing_rt) %>%
  count() %>%
  group_by(drop_all_missing_rt) %>%
  count()

test <-
  test %>% 
  left_join(., rt_all_missing, by = "participant_id") %>% 
  filter(drop_all_missing_rt == 0L) # Dropping trials
```

# Exclude each first test trial of every participant before calculating mean response times

* 1: First trial for each participant

```{r}
test <-
  test %>% 
  filter(!is.na(is_prev_congruent)) # 1 trial level exclusion criteria
```

# Calucalte the mean response time and SD for exclusion

```{r calculate mean response time}
rt_participant_outliers <-
  test %>% 
  group_by(participant_id) %>% 
  summarise(rt_participant_mean = mean(rt, na.rm = T),
            rt_participant_sd = sd(rt, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(rt_grand_mean = mean(rt_participant_mean, na.rm = T),
         rt_grand_sd = sd(rt_participant_mean, na.rm = T))

rt_trial_outliers <-
  test %>% 
  ungroup() %>% 
  group_by(participant_id, is_congruent, is_prev_congruent) %>% 
  summarise(rt_conditional_mean = mean(rt, na.rm = T),
            rt_conditional_sd = sd(rt, na.rm = T))

test <-
  test %>% 
  left_join(., rt_participant_outliers, by = "participant_id")

test <-
  test %>% 
  left_join(., rt_trial_outliers, by = c("participant_id", "is_congruent", "is_prev_congruent"))
```

# Create variable that stores whether a participant or a trial should be dropped based on the rt criteria

```{r}
test <-
  test %>% 
  group_by(participant_id) %>% 
  mutate(drop_trial_rt = case_when(rt_conditional_mean + 2.5 * rt_conditional_sd < rt ~ 1L,
                                   rt_conditional_mean - 2.5 * rt_conditional_sd > rt ~ 1L,
                                   TRUE ~ 0L),
         is_prev_drop_trial_rt = case_when(trial_id > 24 & lag(drop_trial_rt) == 1L ~ 1L,
                                           trial_id > 24 & lag(drop_trial_rt) == 0L ~ 0L),
         drop_participant_rt = case_when(rt_grand_mean + 2.5 * rt_grand_sd < rt_participant_mean ~ 1L,
                                         rt_grand_mean - 2.5 * rt_grand_sd > rt_participant_mean ~ 1L,
                                         TRUE ~ 0L))
```

# Exclude participants younger than 18 or older than 99

```{r}
test <-
  test %>% 
  mutate(age_drop = case_when(age < 18 ~ 1L,
                              age > 99 ~ 1L,
                              TRUE ~ 0L)) %>% 

  filter(age_drop != 1L)
```

# Participant level exclusion

* 1: mean accuracy on their respective task was below 70%
* 2: mean reaction time was more than 2.5 SDs away from the mean of their group

```{r participant level exclusion}
test <-
  test %>% 
  filter(drop_participant_acc == 0L,
         drop_participant_rt  == 0L)
```

# Trial level exclusion for rt analysis

* 2: Error trials
* 3: Trials following error trials
* 4: Outliers, trials 2.5 SDs away from the conditional mean of the participant
* 5: Trials following outlier trials

```{r trial level exclusion reaction time}
response_rt_analysis <-
  test %>% 
  filter(is_correct            == 1L,   # 2 exclusion criteria
         is_prev_correct       == 1L,   # 3 exclusion criteria
         drop_trial_rt         == 0L,   # 4 exclusion criteria
         is_prev_drop_trial_rt == 0L)   # 5 exclusion criteria
```

# Proportion of dropped trials
```{r}
trial_dropped_prop =  1 - (nrow(response_rt_analysis) / nrow(test)) 

```

# Trial level exclusion for error analysis

* 2: Outliers, trials 2.5 SDs away from the conditional mean of the participant
* 3: Trials following outlier trials

```{r trial level exclusion error}
response_acc_analysis <-
  test %>%
  filter(drop_trial_rt         == 0L, # 2 exclusion criteria
         is_prev_drop_trial_rt == 0L) # 3 exclusion criteria
```

# Trial level exclusion for exploratory error analysis

* 2: Outliers, trials 2.5 SDs away from the conditional mean of the participant
* 3: Trials following outlier trials
* 4: Trials following error trials (requested by reviewer)

```{r trial level exclusion exploratory error}
response_acc_exp_analysis <-
  test %>% 
  filter(drop_trial_rt         == 0L, # 2 exclusion criteria
         is_prev_drop_trial_rt == 0L, # 3 exclusion criteria
         is_prev_correct       == 1L) # 4 exclusion criteria
```

# Save task to individual dataframes

```{r save tasks}
# Saving data for the reaction time analysis
write_tsv(response_rt_analysis, file.path(current_version, "data", "Processed", "flanker_processed_rt.tsv"))

# Saving data for the accuracy analysis
write_tsv(response_acc_analysis, file.path(current_version, "data", "Processed", "flanker_processed_acc.tsv"))

# Saving data for the exploratory accuracy analysis
#write_tsv(response_acc_exp_analysis, file.path(current_version, "Data", "Processed", "ppc_processed_acc_exploratory.tsv"))
```

Final tsv files were uploaded to OSF manually.