---
title: "Prime Probe CSE: Analysis"
author: "Miklos Bognar"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r load packages, warning = FALSE, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, osfr, lme4,lmerTest, BayesFactor, DescTools, sjstats, car, broom, papaja)
```

# Load helper functions

```{r load helper functions}
source("../utils.R")
```

# Current version of the design

```{r}
current_version <- "global_core_primeprobe"
```

Currently we are working with the following version of the design: `r str_extract(current_version, "[^/]+$")`

# Create local data structure

```{r}
local_data_pth <- file.path(current_version, "Data")

create_local_structure(local_data_pth)
```

# Remove local data

Uncomment the following lines to remove the local Source data if needed.

```{r}
# local_data_pth <- file.path(current_version, "Data")

# remove_local_data(local_data_pth)
```


# Import data

```{r, message = FALSE, warning = FALSE}
# Reaction time
processed_rt <- read_tsv(file.path(current_version, "data", "processed", "prime_probe_global_processed_rt.tsv"))

# Accuracy
processed_acc <- read_tsv(file.path(current_version, "Data", "Processed", "prime_probe_global_acc.tsv"))

```

# Descriptive statistics of the sample size
## Number of participants left after exclusion

The number of participants is the same for the reaction time, the accuracy, and the exploratory analyses as well.

```{r}
processed_rt %>% 
  distinct(participant_id) %>% 
  count()
```

## Number of responses after exclusion
### For the reaction time analysis

```{r}
processed_rt %>%
  count()
```

### For the accuracy analysis

```{r}
processed_acc %>% 
  count()
```


## Age

We calculated the following statistics based on the reaction time data file, but because it contains the same participants as the accuracy data, and the exploratory data files there should be no difference between the results.

```{r}
processed_rt %>% 
  distinct(participant_id, .keep_all = T) %>% 
  summarize(median_age = median(age, na.rm = T),
            min_age = min(age, na.rm = T),
            max_age = max(age, na.rm = T),
            quart1_age = quantile(age, probs = 0.25, na.rm = T),
            quart3_age = quantile(age, probs = 0.75, na.rm = T)) %>% 
  knitr::kable(caption = "Age demographics")
```

## Gender

```{r}
processed_rt %>% 
  distinct(participant_id, .keep_all = T) %>% 
  group_by(gender) %>% 
  count() %>% 
  ungroup() %>% 
  filter(gender %in% c("female", "male")) %>% 
  mutate(prop = n / sum(n) * 100) %>% 
  knitr::kable(caption = "Gender demographics")
```

## Education demographics

```{r}
processed_rt %>% 
  distinct(participant_id, .keep_all = T) %>% 
  group_by(education) %>% 
  count() %>% 
  ungroup() %>% 
  filter(education %ni% c("blank", "refused")) %>% 
  mutate(prop = n / sum(n) * 100) %>% 
  knitr::kable(caption = "Education demographics")
```

# Number of different primeprobe feature pairs

```{r}
processed_rt %>% 
  mutate(condition = case_when(is_prev_congruent == 0L & is_congruent == 0L ~ "ii",
                               is_prev_congruent == 0L & is_congruent == 1L ~ "ic",
                               is_prev_congruent == 1L & is_congruent == 0L ~ "ci",
                               is_prev_congruent == 1L & is_congruent == 1L ~ "cc",
                               TRUE ~ NA_character_),
         response_hand = case_when(probe %in% c("bal", "jobb") ~ "slow",
                          probe %in% c("fel", "le") ~ "fast")) %>% 
  group_by(response_hand, condition) %>% 
  summarize(n = n(),
           mean_rt = mean(rt),
           sd_rt = sd(rt, na.rm = T),
           se_rt = sd_rt / sqrt(n))
```

# Figures of CSE
## For the reaction time data

```{r}
# Prepare data for plotting
cse_plot_rt_data <- 
  processed_rt %>% 
  mutate(is_prev_congruent = case_when(is_prev_congruent ==  0L ~ "Incongruent",
                                     is_prev_congruent ==  1L ~ "Congruent"),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_prev_congruent, is_congruent) %>% 
  summarise(participant_mean_rt = mean(rt, na.rm = T)) %>% 
  group_by(is_prev_congruent, is_congruent) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

# Create the plot
cse_plot_rt <- 
  cse_plot_rt_data %>% 
  ggplot() +
  aes(x = is_prev_congruent,
                 y = mean_rt,
                 shape = is_congruent,
                 group = is_congruent) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(550, 800)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Congruency of the previous trial")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "Congruency of \n the current trial")) +
  papaja::theme_apa() + #not on cran, so if you don't want to install it manually, just comment this line out
  theme(legend.position = c(0.5,0.85),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        )

# Print the plot
cse_plot_rt
```

## Saving the figure

```{r}
ggsave(file.path(current_version, "prime_probe_global_rt_cse.png"), width = 14.4, height = 8, plot = last_plot())
```

## For the accuracy data

```{r}
# Prepare data for plotting
cse_plot_acc_data <-
  processed_acc %>% 
  mutate(is_prev_congruent = case_when(is_prev_congruent ==  0L ~ "Incongruent",
                                     is_prev_congruent ==  1L ~ "Congruent"),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_prev_congruent, is_congruent) %>% 
  summarise(participant_mean_acc = mean(is_correct, na.rm = T)) %>% 
  group_by(is_prev_congruent, is_congruent) %>% 
  summarise(N = n(),
            mean_acc = mean(participant_mean_acc, na.rm = T),
            sd_acc = sd(participant_mean_acc, na.rm = T),
            se_acc = sd_acc / sqrt(N))

# Create the plot
cse_plot_acc <- 
  cse_plot_acc_data %>%
  ggplot() +
  aes(x = is_prev_congruent,
      y = mean_acc,
      shape = is_congruent,
      group = is_congruent) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc), width=.1) +
  scale_shape_manual(values = c(4, 16)) + 
  scale_y_continuous(limits = c(0.93, 1)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Congruency of the previous trial")+
  ylab("Accuracy") +
  guides(shape = guide_legend(title="Congruency of \n the current trial")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.85, 0.5),
  axis.line = element_line(color = "black"))

# Print the plot
cse_plot_acc
```

## Saving the figure

```{r}
ggsave(file.path(current_version, "prime_probe_global_acc_cse.png"), width = 14.4, height = 8, plot = last_plot())
```

## For the exploratory accuracy data

```{r}
# Prepare data for plotting
cse_plot_acc_exp_data <- 
  processed_acc_exp %>% 
  mutate(is_prev_congruent = case_when(is_prev_congruent ==  0L ~ "Incongruent",
                                     is_prev_congruent ==  1L ~ "Congruent"),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_prev_congruent, is_congruent) %>% 
  summarise(participant_mean_acc = mean(is_correct, na.rm = T)) %>% 
  group_by(is_prev_congruent, is_congruent) %>% 
  summarise(N = n(),
            mean_acc = mean(participant_mean_acc, na.rm = T),
            sd_acc = sd(participant_mean_acc, na.rm = T),
            se_acc = sd_acc / sqrt(N))

# Create the plot
cse_plot_acc_exp <- 
  cse_plot_acc_exp_data %>% 
  ggplot() +
  aes(x = is_prev_congruent,
      y = mean_acc,
      shape = is_congruent,
      group = is_congruent) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc), width = .1) +
  scale_shape_manual(values = c(4, 16)) + 
  scale_y_continuous(limits = c(0.93, 1)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Congruency of the previous trial")+
  ylab("Accuracy") +
  guides(shape = guide_legend(title="Congruency of \n the current trial")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.85, 0.5),
        axis.line = element_line(color = "black"))

# Print the plot
cse_plot_acc_exp
```

## Saving the figure

```{r}
ggsave(file.path(current_version, "Figures", "ppc_acc_exp_cse.png"), width = 14.4, height = 8, plot = last_plot())
```

# Reaction time analyis
## I. analysis: Testing whether the CSE was present in the different tasks
### Preprocessing data

###linear regression analysis for congruency effect

```{r}
library(lmerTest)
rt_random_model <- lmer(rt ~ 1 + (1|filename), data = processed_rt)


congruency_effect_model <- lmer(rt ~ is_congruent + (1|filename), data = processed_rt)
summary(congruency_effect_model)
congruency_effect_model_summary = summary(congruency_effect_model)

```
### Bayesian analysis of congruency effect

```{r}

Bf(sd = congruency_effect_model_summary$coefficients[4],
   obtained = congruency_effect_model_summary$coefficients[2]*-1,
   dfdata = congruency_effect_model_summary$coefficients[6],
   meanoftheory = 0,
   sdtheory = 60,
   dftheory = 10^10,
   tail = 1)


```


### linear regression analysis for interaction
```{r}
rt_random_intercept_model <- lmer(rt ~ is_prev_congruent * is_congruent + (1|filename), data = processed_rt)
random_intercept <- summary(rt_random_intercept_model)

rt_random_intercept_slope_model <- lmer(rt ~ is_prev_congruent * is_congruent + (1 + is_congruent|filename), data = processed_rt)

cs_effect_model <- summary(rt_random_intercept_model)
cs_effect_model
```

### cse bayes factor

### Bayesian analysis of linear regression model
```{r}

Bf(sd = cs_effect_model$coefficients[8],
   obtained = cs_effect_model$coefficients[4]*-1,
   dfdata = cs_effect_model$coefficients[12],
   meanoftheory = 0,
   sdtheory = 30, #0.07,#9298,
   dftheory = 10^10,
   tail = 1)

```

