---
title: "Affective Signaling Prime-probe: Source to Raw Data Cleaning"
author: "Miklos Bognar"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r load packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, osfr, janitor, purrrlyr, lubridate, rstudioapi)
```

# Load helper functions

```{r load helper functions}
source("../utils.R")
```

# Current version of the design

```{r}
# paste here the absolute path to the current data folder
current_version <- "affective_primeprobe_arousal_source_data"
```

Currently we are working with the following version of the design: `r str_extract(current_version, "[^/]+$")`

# Create local data structure

```{r}
local_data_pth <- file.path(current_version, "data") # the directory containing all source data files

create_local_structure(local_data_pth)
```

# Remove local data

Uncomment the following lines to remove the local Source data if needed.

```{r}
# remove_local_data(local_data_pth)
```

We will read the source data from a private repository because the datafiles contain personal data.

# Import and merge data

```{r import and merge data}
# Read in datafiles
source <- read_plus(pattern = ".csv$",
                    path = file.path(local_data_pth),
                    # include = "2020") %>% 
                    include = "2021") %>% 
  janitor::clean_names()

# Read in demographic data
demographics <- read_csv(file.path(local_data_pth, "demographics.csv")) %>% 
  janitor::clean_names()

# Read in participant identifiers data
#participant_id <- read_csv(file.path(current_version,"private/b29_participant-metadata.csv")) %>% 
 # janitor::clean_names()
participant_id <- read_csv(file.path(current_version,"private/participant-metadata.csv")) %>% 
  janitor::clean_names()
```

# Filter private data

Keep only rows from the current version of the experiment.

```{r}
participant_id <-
  participant_id %>% 
  filter(task == "affective_words_primeprobe") 

```

# Participant level exclusion

* 1: The recorded response is only a response coming from testing the program
* 2: The unique identifier is missing
* 3: There are multiple responses from one participant (we only keep the first)

## Number of responses

```{r number of responses}
participant_id %>% 
  count()
```

## Number of responses after the first exclusion

How many participants do we have when we just remove testing responses.

```{r}
# UserIds to be deleted because they are responses from testing the program
trial_response_id <- 
  participant_id %>% 
  mutate(trial_drop = case_when(version %in% c("test","inlab_test") ~ 1L,
                                user_id %in% c("a","sfafas","test","sa") ~ 1L,
                                TRUE ~ 0L)) %>%
  filter(trial_drop == 1L) %>% 
  pull(user_id)

participant_id %>% 
  filter(user_id %ni% trial_response_id) %>% 
  count()
```

## Number of responses after the second exclusion 

How many participants do we have when we just remove testing responses and missing user ids.

```{r number of responses after second exlusion}
participant_id %>% 
  filter(user_id %ni% trial_response_id) %>% 
  filter(!is.na(user_id)) %>%
  count()
```

## Number of responses after the third exclusion

How many responses do we have after every exclusion.

```{r number of responses after third exlusion}
participant_id %>% 
  filter(user_id %ni% trial_response_id) %>% 
  filter(!is.na(user_id)) %>%
  distinct(user_id, .keep_all = TRUE) %>% 
  count()
```

### Checking the duplicate responses

Number of responses per participant.

```{r number of responses per participant}
participant_id %>% 
  group_by(user_id) %>% 
  count()
```

Save participants who completed the task more than once.

```{r save duplicates}
participant_duplicate <- 
  participant_id %>% 
  filter(user_id %ni% trial_response_id) %>% 
  filter(!is.na(user_id)) %>%
  group_by(user_id) %>% 
  count() %>% 
  filter(n != 1)

participant_duplicate %>% knitr::kable(caption = "Number of duplicate responses")
```

Show the descriptive data of the duplicate responses.

```{r duplicate descriptive}
participant_duplicate <- 
  participant_id %>% 
  filter(user_id %in% pull(participant_duplicate, user_id)) %>%
  mutate(consent_time = as_datetime(consent_time / 1000, tz = "Europe/Prague")) %>% 
  select(user_id,
         loc,
         id,
         task,
         consent_time)

participant_duplicate %>%
  knitr::kable(caption = "Duplicate responses")
```

Flag the datafile that will be dropped because it is a duplicate.

```{r}
participant_duplicate <- 
  participant_duplicate %>% 
  arrange(consent_time) %>% 
  group_by(user_id) %>% 
  mutate(duplicate_id = row_number()) %>% 
  ungroup() %>% 
  mutate(duplicate_drop = case_when(duplicate_id != 1 ~ 1L,
                                    TRUE ~ NA_integer_))

participant_id <-
  participant_id %>% 
  left_join(., select(participant_duplicate, user_id, id, duplicate_drop), by = c("user_id", "id"))
```

# Join demographics data with responses

```{r join demographic data}
source <- 
  source %>%
  left_join(., demographics, by = c("id"))
```

# Join data with participant_id

```{r join participant id}
source <- 
  source %>%
  left_join(., participant_id, by = c("id"))
```

# Delete trial responses

```{r delete trial responses}
source <-
  source %>% 
  filter(user_id %ni% trial_response_id)
```

# Delete cases where the user_id is missing

```{r delete empty userid}
source <- 
  source %>% 
  filter(!is.na(user_id))
```

# Delete multiple responses

We are keeping only the first response from the participants who participated in the experiment several times.

```{r drop duplicates}
source <- 
  source %>% 
  filter(is.na(duplicate_drop))
```

# Deidentify participants

We need to remove any information that might identify the participants

```{r deidentify participants}
source <- 
  source %>% 
  select(-user_id, -debrief_general_comments, -duplicate_drop)
```

# Rename "id" variable to "participant_id"

```{r}
source <- 
  source %>% 
  rename(participant_id = id)
```

# Save each task separately

```{r save tasks}
write_tsv(source, file.path(current_version, "data", "Raw", "aspp_arousal_raw_data.tsv"))
```