---
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r load packages, warning = FALSE, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, osfr, lme4, lmerTest, BayesFactor, DescTools, sjstats, car, broom, papaja)
```

# Load helper functions

```{r load helper functions}
source("../utils.R")
```

# Current version of the design

```{r}
current_version <- "affective_flanker_arousal_source_data"
```

Currently we are working with the following version of the design: `r str_extract(current_version, "[^/]+$")`

# Create local data structure

```{r}
local_data_pth <- file.path(current_version, "data")

create_local_structure(local_data_pth)
```

# Import data

```{r, message = FALSE, warning = FALSE}
# Reaction time
processed_rt <- read_tsv(file.path(current_version, "data", "Processed", "flanker_arousal_processed_rt.tsv"))

# Accuracy
processed_acc <- read_tsv(file.path(current_version, "data", "Processed", "flanker_arousal_processed_acc.tsv"))


processed_rt_nmin3 <- read_tsv(file.path(current_version, "data", "Processed", "flanker_arousal_processed_rt_nmin3.tsv"))
```

# Descriptive statistics of the sample size
## Number of participants left after exclusion

The number of participants is the same for the reaction time, the accuracy, and the exploratory analyses as well.

```{r}
processed_rt %>% 
  distinct(participant_id) %>% 
  count()
```

## Number of responses after exclusion
### For the reaction time analysis

```{r}
processed_rt %>%
  count()
```

### For the accuracy analysis

```{r}
processed_acc %>% 
  count()
```


## Age

We calculated the following statistics based on the reaction time data file, but because it contains the same participants as the accuracy data, and the exploratory data files there should be no difference between the results.

```{r}
processed_rt %>% 
  distinct(participant_id, .keep_all = T) %>% 
  summarize(median_age = median(age, na.rm = T),
            min_age = min(age, na.rm = T),
            max_age = max(age, na.rm = T),
            quart1_age = quantile(age, probs = 0.25, na.rm = T),
            quart3_age = quantile(age, probs = 0.75, na.rm = T)) %>% 
  knitr::kable(caption = "Age demographics")
```

## Gender

```{r}
processed_rt %>% 
  distinct(participant_id, .keep_all = T) %>% 
  group_by(gender) %>% 
  count() %>% 
  ungroup() %>% 
  filter(gender %in% c("female", "male")) %>% 
  mutate(prop = n / sum(n) * 100) %>% 
  knitr::kable(caption = "Gender demographics")
```

## Education demographics

```{r}
processed_rt %>% 
  distinct(participant_id, .keep_all = T) %>% 
  group_by(education) %>% 
  count() %>% 
  ungroup() %>% 
  filter(education %ni% c("blank", "refused")) %>% 
  mutate(prop = n / sum(n) * 100) %>% 
  knitr::kable(caption = "Education demographics")
```


# Figures of CSE
## For the reaction time data

```{r}
# Prepare data for plotting
cse_plot_rt_data <- 
  processed_rt %>% 
  mutate(is_prev_cong = case_when(is_prev_cong ==  0L ~ "High",
                                  is_prev_cong ==  1L ~ "Low"),
         is_prev_cong = as_factor(is_prev_cong),
         is_prev_cong = fct_relevel(is_prev_cong, c("Low", "High")),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_prev_cong, is_congruent) %>% 
  summarise(participant_mean_rt = mean(rt, na.rm = T)) %>% 
  group_by(is_prev_cong, is_congruent) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

# Create the plot
cse_plot_rt <- 
  cse_plot_rt_data %>% 
  ggplot() +
  aes(x = is_prev_cong,
                 y = mean_rt,
                 shape = is_congruent,
                 group = is_congruent) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(750, 1200)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Arousal of the previous word")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "Congruency of \n the current trial")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.5,0.25),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        )
# Print the plot
cse_plot_rt
```

## Saving the figure

```{r}
ggsave(file.path(current_version,"figures/flanker_arousal_rt_cse.png"), width = 14.4, height = 8, plot = last_plot())
```

## For the accuracy data

```{r}
# Prepare data for plotting
cse_plot_acc_data <-
  processed_acc %>% 
  mutate(is_prev_congruent = case_when(is_prev_congruent ==  0L ~ "Incongruent",
                                     is_prev_congruent ==  1L ~ "Congruent"),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_prev_congruent, is_congruent) %>% 
  summarise(participant_mean_acc = mean(is_correct, na.rm = T)) %>% 
  group_by(is_prev_congruent, is_congruent) %>% 
  summarise(N = n(),
            mean_acc = mean(participant_mean_acc, na.rm = T),
            sd_acc = sd(participant_mean_acc, na.rm = T),
            se_acc = sd_acc / sqrt(N))

# Create the plot
cse_plot_acc <- 
  cse_plot_acc_data %>%
  ggplot() +
  aes(x = is_prev_congruent,
      y = mean_acc,
      shape = is_congruent,
      group = is_congruent) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc), width=.1) +
  scale_shape_manual(values = c(4, 16)) + 
  scale_y_continuous(limits = c(0.93, 1)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Congruency of the previous trial")+
  ylab("Accuracy") +
  guides(shape = guide_legend(title="Congruency of \n the current trial")) +
#  papaja::theme_apa() +
  theme(legend.position = c(0.85, 0.5),
  axis.line = element_line(color = "black"))

# Print the plot
cse_plot_acc
```

## Saving the figure

```{r}
ggsave(file.path(current_version, "Figures", "ppc_acc_cse.png"), width = 14.4, height = 8, plot = last_plot())
```


# Reaction time analyis
## I. analysis: Testing whether the CSE was present in the different tasks
### Preprocessing data


### linear regression analysis
```{r}
library(lmerTest)
rt_random_model <- lmer(rt ~ 1 + (1|filename), data = processed_rt)

rt_random_intercept_model_no_interaction <- lmer(rt ~ is_prev_congruent + is_congruent + (1|filename), data = processed_rt)
congruency_model <- lmer(rt ~ is_congruent + (1|filename), data = processed_rt)
congruency_model = summary(congruency_model)
congruency_model
rt_random_intercept_model <- lmer(rt ~ is_prev_cong * is_congruent + (1|filename), data = processed_rt)
random_intercept <- summary(rt_random_intercept_model)

rt_random_intercept_slope_model <- lmer(rt ~ is_prev_cong * is_congruent + (1 + is_congruent|filename), data = processed_rt)

summary(rt_random_intercept_slope_model)
test_model = summary(rt_random_intercept_slope_model)
```

### Bayesian analysis of the linear regression model of congruency effect
sd prior: Weissman (2014) congruency effect -> 53ms
```{r}

Bf(sd = congruency_model$coefficients[4],
   obtained = congruency_model$coefficients[2]*-1,
   dfdata = congruency_model$coefficients[6],
   meanoftheory = 0,
   sdtheory = 53,
   dftheory = 10^10,
   tail = 1)

```


### Bayesian analysis of linear regression model of sequential congruency effect (interaction between current and previous congruency)
sd prior: Weissman (2014) congruency effect/2 -> 53/2 = 26.5
```{r}

Bf(sd = test_model$coefficients[8],
   obtained = test_model$coefficients[4]*-1,
   dfdata = test_model$coefficients[12],
   meanoftheory = 0,
   sdtheory = 26.5,#1000000,#9.29,#26.5,
   dftheory = 10^10,
   tail = 1)

```

#### CE bf on the same linear regression
```{r}

Bf(sd = test_model$coefficients[7],
   obtained = test_model$coefficients[3]*-1,
   dfdata = test_model$coefficients[11],
   meanoftheory = 0,
   sdtheory = 22969,#22969,#1.29,53
   dftheory = 10^10,
   tail = 1)

```


### Exploratory analysis of sequential congruency effects with arousal

```{r}
cse_plot_rt_data_cohen <- 
  processed_rt_nmin3 %>% 
  mutate(is_prev_cong = case_when(is_prev_cong ==  0L ~ "High",
                                  is_prev_cong ==  1L ~ "Low"),

         is_prev_cong = fct_relevel(is_prev_cong, c("Low", "High")),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent"),
         n_min3_cong = case_when(n_min3_cong ==  0L ~ "Incongruent",
                                 n_min3_cong ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_prev_cong, is_congruent, n_min3_cong) %>% 
  summarise(participant_mean_rt = mean(rt, na.rm = T)) %>% 
  group_by(is_prev_cong, is_congruent, n_min3_cong) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

# Create the plot
cse_plot_rt_cohen <- 
  cse_plot_rt_data_cohen %>% 
  ggplot() +
  aes(x = is_prev_cong,
                 y = mean_rt,
                 shape = is_congruent,
                 group = is_congruent) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(750, 1200)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Arousal of the previous word")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "Congruency of \n the current trial")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.5,0.25),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        ) +
  facet_grid(cols = vars(n_min3_cong))
# Print the plot
cse_plot_rt_cohen

ggsave(file.path(current_version,"figures/cse_plot_rt_cohen.png"), width = 14.4, height = 8, plot = last_plot())
```


```{r}
cse_plot_rt_data_cohen2 <- 
  processed_rt_nmin3 %>% 
  mutate(is_prev_cong = case_when(is_prev_cong ==  0L ~ "High",
                                  is_prev_cong ==  1L ~ "Low"),

         is_prev_cong = fct_relevel(is_prev_cong, c("Low", "High")),
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent"),
         n_min3_cong = case_when(n_min3_cong ==  0L ~ "Incongruent",
                                 n_min3_cong ==  1L ~ "Congruent")) %>%
  group_by(participant_id, is_prev_cong, n_min3_cong) %>% 
  summarise(participant_mean_rt = mean(rt, na.rm = T)) %>% 
  group_by(is_prev_cong,  n_min3_cong) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))


cse_plot_rt_cohen2 <- 
  cse_plot_rt_data_cohen2 %>% 
  ggplot() +
  aes(x = n_min3_cong,
                 y = mean_rt,
                 shape = is_prev_cong,
                 group = is_prev_cong) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(900, 1100)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Congruency of the n-3 trial")+
  ylab("Reaction time of current trial") +
  guides(shape = guide_legend(title = "Arousal of the previous trial")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.5,0.75),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22),
        ) 

cse_plot_rt_cohen2

cohen2_model = lmer(rt ~ n_min3_cong * is_prev_cong + (1|filename), data = processed_rt_nmin3)
summary(cohen2_model)

ggsave(file.path(current_version,"figures/cse_plot_rt_cohen2.png"), width = 14.4, height = 8, plot = last_plot())

```



```{r}
cse_plot_3way_nmin4_data <- 
  processed_rt_nmin3 %>% 
  filter(!is.na(n_min4_arousal)) %>% 
  mutate(is_prev_cong = case_when(is_prev_cong ==  0L ~ "High",
                                  is_prev_cong ==  1L ~ "Low"),
         
         is_prev_cong = fct_relevel(is_prev_cong, c("Low", "High")),
         
         is_congruent = case_when(is_congruent ==  0L ~ "Incongruent",
                                 is_congruent ==  1L ~ "Congruent"),
n_min3_cong = case_when(n_min3_cong ==  0L ~ "Incongruent",
                                 n_min3_cong ==  1L ~ "Congruent"),
n_min4_arousal = case_when(n_min4_arousal ==  0L ~ "High",
                                  n_min4_arousal ==  1L ~ "Low"),
n_min4_arousal = fct_relevel(n_min4_arousal, c("Low", "High")),)%>%
  
  group_by(participant_id, is_congruent, n_min3_cong, n_min4_arousal) %>% 
  summarise(participant_mean_rt = mean(rt, na.rm = T)) %>% 
  group_by(is_congruent, n_min3_cong, n_min4_arousal) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

cse_plot_3way_nmin4 <- 
  cse_plot_3way_nmin4_data %>% 
  ggplot() +
  aes(x = n_min3_cong,
                 y = mean_rt,
                 color = is_congruent,
      
                 group = is_congruent) +
  geom_path() +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_y_continuous(limits = c(750, 1200)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("nmin3 congruency")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "current congruency")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.5,0.25),
        legend.title = element_text(size= 26),
        legend.text=element_text(size=24),
        axis.line = element_line(color = "black",size=1),
        axis.title = element_text(size=24),
        axis.text = element_text(size=22)
        )+
  facet_grid(cols = vars(n_min4_arousal))

cse_plot_3way_nmin4

ggsave(file.path(current_version,"figures/cse_plot_3way_nmin4.png"), width = 14.4, height = 8, plot = last_plot())

```

```{r}
threeway_model = lmer(rt ~ is_congruent * n_min3_cong * n_min4_arousal + (1|filename), data = processed_rt_nmin3)
summary(threeway_model)

negative_processed = processed_rt_nmin3 %>% 
  filter(n_min4_arousal == 0)

cse_high_arousal_nmin4 = lmer(rt ~ is_congruent * n_min3_cong + (1|filename), data = negative_processed)
summary(cse_high_arousal_nmin4)
```

